### 2019-04-29 monograph/thesis/chapters/introduction.tex
Translated 2 new paragraphs on introduction.tex

\lang{%
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did \cite{quitDiffCalculating}.
    Hence, if every programmer re\hyp{}writes the history making changes
    like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines. \cite{findingRegressionsInProjects}
}{%
    Estas conclusões devem\hyp{}se por que ao trabalhar com um sistema de versionamento como `git',
    recomenda\hyp{}se manter todo o código sobre um único stilo,
    ou aquilo que conhece\hyp{}se ``Boas Práticas'' colocado como um padrão a todos.
    Segue\hyp{}se isso devido aos problemas gerado ao permitir
    que cada programador escreva como lhe agrada melhor.
    Se cada um escreve como bem entende,
    irá existir ruídos de formação em abundância espalhados por tudo o código\hyp{}fonte,
    o quê complicará a revisão de código,
    dificultando entender o que cada programador fez \cite{quitDiffCalculating}.

    \cite{findingRegressionsInProjects}
}

\lang{%
    Talking about the last ideia pointed out, we could also think about an
    approach to creating a new version control system which focuses only on
    significant changes to the code, while reviewing code changes. However, this
    approach could not be ideal, as for example, it would allow programmers to
    start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code
    re\hyp{}adding new lines before each one of your beloved if\s, just because some
    night shift programmer\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}}
    had just removed them?
}{%

>>>>

\lang{%
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did \cite{quitDiffCalculating}.
    Hence, if every programmer re\hyp{}writes the history making changes
    like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines. \cite{findingRegressionsInProjects}
}{%
    Estas conclusões devem\hyp{}se por que ao trabalhar com um sistema de versionamento como `git',
    recomenda\hyp{}se manter todo o código sobre um único stilo,
    ou aquilo que conhece\hyp{}se ``Boas Práticas'' colocado como um padrão a todos.
    Segue\hyp{}se isso devido aos problemas gerado ao permitir
    que cada programador escreva como lhe agrada melhor.
    Se cada um escreve como bem entende,
    irá existir ruídos de formação em abundância espalhados por tudo o código\hyp{}fonte,
    o quê complicará a revisão de código,
    dificultando entender o que cada programador fez \cite{quitDiffCalculating}.
    Portando,
    caso todos os programadores decidam re~=escrever o histórico,
    fazendo mudanças como inserindo novas linhas antes de cada `if':
    \begin{enumerate}
        \item Eles irão disperdiçar um tempo que eles poderiam estar utilizando para escrever código.
        \item O histórico git irá conter ruídos desnecessários,
        pois o foco de um sistema de versionamento são conter mudanças se sejam significantes,
        como criações de novas funções,
        correção de bugs, etc. \cite{findingRegressionsInProjects}
    \end{enumerate}
}

\lang{%
    Talking about the last ideia pointed out, we could also think about an
    approach to creating a new version control system which focuses only on
    significant changes to the code, while reviewing code changes. However, this
    approach could not be ideal, as for example, it would allow programmers to
    start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code
    re\hyp{}adding new lines before each one of your beloved if\s, just because some
    night shift programmer\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}}
    had just removed them?
}{%
    Sobre a última ideia apontada,
    poderíamos também pensar em uma abordagem para criar um novo sistema de controle de versão,
    que foca apenas mudanças significativas no código enquanto faz-se a revisão das mudanças no código.
    No entanto,
    essa abordagem poderia não ser ideal,
    pois, por exemplo,
    permitiria que os programadores iniciassem guerras tediosas de ajustes de código improdutivos.
    Por exemplo,
    imagine como seria se todo os dias você tivesse que passar pelo código
    re~=adicionando novas linhas antes de cada um dos seus amados if\s,
    só porque algum programador
    do turno da
    noite\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}}
    tinha acabado de
    removê-los?
}
